Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-12-27 doc/paper.Rmd
.

From initial tests the amount of movement to get new windows left and right of the original same shift window seems to directly influence the
penultimate pvalue and U statistic that we look at.

So the question that arises is how much of a movement is reasonable and should be used?
Is there a way to understand if the 2nd marking in comparison to the 1st marking is compressed or elongated? Should the amount of movement selected depend on this compression or elongation? or using a static delta movement value justifieable.

>>>>

From initial tests the amount of movement to get new windows left and right of the original same shift window seems to directly influence the
the pvalue and U statistic that we look at.

### how much of a movement is reasonable and should be used?
Is there a way to understand if the 2nd marking in comparison to the 1st marking is compressed or elongated or neither? Should the amount of movement selected depend on this compression or elongation? or using a static delta movement value justifieable.
